How Important are Usage Examples in REST API Documentation?

### 2017-02-27 controlled_study.tex
better ending sentence

\subsubsection{Measuring API Usability}
Several papers have been published on the topic of measuring API usability. Rama et al. presented a set of formulas for computing a measure of API usability based on the API's structural components such as classes, methods, parameters, return values, thread-safety, etc \cite{rama}. Scheller et al. presented a framework for automatically measuring the complexity of an API \cite{scheller2015automated}. They identified a list of measurable API properties and provided formulas to compute complexities related to the interfaces, implementation and setup of an API. Grill et al. proposed an HCI based approach that can be used by API developers to understand and improve on the problem areas related to an API \cite{Grill2012}. They suggested using a combination of expert opinion and developer workshops on APIs to identify and collect feedback about API and its documentation related problems. In our work, we've focused on the usability related properties of an API and proved relationship between API client developer success and the presence of usage examples on API documentation.

>>>>

\subsubsection{Measuring API Usability}
Several papers have been published on the topic of measuring API usability. Rama et al. presented a set of formulas for computing a measure of API usability based on the API's structural components such as classes, methods, parameters, return values, thread-safety, etc \cite{rama}. Scheller et al. presented a framework for automatically measuring the complexity of an API \cite{scheller2015automated}. They identified a list of measurable API properties and provided formulas to compute complexities related to the interfaces, implementation and setup of an API. Grill et al. proposed an HCI based approach that can be used by API developers to understand and improve on the problem areas related to an API \cite{Grill2012}. They suggested using a combination of expert opinion and developer workshops on APIs to identify and collect feedback about API and its documentation related problems. In our work, instead of measuring overall API usability, we have focused specifically on the relationship of REST API usability with respect to usage examples.
